MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives

### 2017-09-19 ArticleRevision/article_with_markings/atricle_with_markings.tex
Made changes according to Alberto + ran spell checker. Going to copy these to dropbox so he can submit it later.

\section{Introduction}\label{intro}
In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns between training samples and their class label. \textit{Multi-instance} (MI) learning is a generalization of \textit{supervised learning} that has been recently been gaining interest because \hl{of its applicability to many real-world problems such as webmining and text categorization {\citep{Andrews2002}}, image classification and retreival} {\citep{Herman2008,qi2007}}, \hl{human action recognition {\citep{Yi2016}}, medical diagnosis and imaging {\citep{Herrera2016}}, and bioinformatics {\citep{Dietterich1997}} (drug activity prediction and protein identification).}

@@

For most of the methods described above, implicit or explicit assumptions have been made about the distribution of the data. Selecting a method that is robust for a problem such as MIL can be difficult when little is known about the nature of the data, especially considering the unknown distribution of the instances within bags~\citep{2015-KAIS,2016-INS-MIARM}. \hl{MIRSVM, is an iterative method that uses SVMs to design a MIL model without making prior assumptions about the data. Classifiers of this type are known to provide better generalization capabilities, performance, and sparser models.}

@@

\section{Multiple-Instance Representative SVM}\label{sec:contribution}
MIRSVM is based on the idea of selecting representative instances from both positive and negative bags which are used to find an unbiased, optimal separating hyperplane. A representative is iteratively chosen from each bag, and a new hyperplane is formed according to the representatives until they converge. Based on the SMI hypothesis, only one instance in a bag is required to be positive for the bag to adopt a positive label. Due to the unknown distribution of instances within positive bags, MIRSVM is designed to give preference to negative bags during training, because their distribution is known, i.e. all instances are guaranteed to be negative. This is evident during the representative selection process, by taking the index of the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{argmax}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$, \hl{where $\bm w \in \reals^d$ is a $d$-dimensional weight vector, $b \in \reals$ is a bias term.} In other words, the most positive instance is chosen from each positive bag and the least negative instance is chosen from each negative bag (instances with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags. Equation~\eqref{eq:primalmirsvm} presents the primal MIRSVM optimization problem:
\begin{subequations} 
\label{eq:primalmirsvm}
\begin{alignat}{2}
\min\limits_{\bm w, b,\bm\xi}& {\,\,} \frac{1}{2}||\bm{w}||^2 + \frac{C}{n}\sum_I \xi_I, \tag{\ref{eq:primalmirsvm}}\\ 
\text{s.t.}& {\,\,} Y_I(\langle\bm{w},\bm x_{s_I}\rangle + b) \geq 1 - \xi_I,\, \forall I \in \set{1,\ldots,n}  \label{eq:primalmirsvm1}\\
{} & {\,\,} \xi_I \geq 0,\, \forall I \in \set{1,\ldots,n}, 
\end{alignat}
\end{subequations} 
\hl{where $\bm S_I$ is a set of the bag representatives' indices, $\bm x_{s_I}$ is the instance representative of bag $\mathcal{B}_I$, and the slack variable $\bm \xi \in \reals^m$ allows for optimizing over bag errors. Note the variables in MIRSVMs formulation are the similar to those of the traditional SVM, except they are now representing each bag as an instance.}

Solving the optimization problem given in Equation~\eqref{eq:primalmirsvm} using a quadratic programming solver is a computationally expensive task due to the number of constraints, which scales by the number of bags $n$, as well as the calculation of the inner product between two $d$-dimensional vectors in constraint~\eqref{eq:primalmirsvm1}. The proposed solution for these problems was deriving and solving the dual of the optimization problem given by Equation~\eqref{eq:primalmirsvm}. The dual can be formed by taking the Lagrangian of~\eqref{eq:primalmirsvm}, given by Equation~\eqref{eqn:svmlagrangian}, where $\bm \alpha$ and $\bm \beta$ are the non-negative Lagrange multipliers.
\begin{equation}
\centering \label{eqn:svmlagrangian}
\resizebox{.9\textwidth}{!}{$
\begin{aligned}
\mathcal{L}\left(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}\right) = \frac{1}{2}\sum_{j=1}^d w_j^2  + \frac{C}{n}\sum_I \xi_I - \sum_I{\beta_I \xi_I} - \sum_I{\alpha_I\left(Y_I\left(\sum_{j=1}^d w_j x_{s_Ij} + b\right) -1 + \xi_I\right)}
\end{aligned}$} 
\end{equation}

At optimality~\citep{Boyd2004}, $\bigtriangledown_{w,b,\xi}\mathcal{L}(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}) = 0$ and the following conditions are met:
\begin{align}
&\frac{\partial\mathcal{L}}{\partial w_j}: w_j = \sum_I{\alpha_I\,Y_I\, x_{s_I\,j}},\,\forall j \in \{1,\ldots,d\}\label{eqn:optcond1}\\
&\frac{\partial\mathcal{L}}{\partial b}: \sum_I{\alpha_IY_I} = 0,\label{eqn:optcond2}\\
&\frac{\partial\mathcal{L}}{\partial\xi_I}: \alpha_I + \beta_I = \frac{C}{n},\,\forall I \in \set{1,\ldots,n}\label{eqn:optcond3} 
\end{align}

By substituting Equations~\eqref{eqn:optcond1},~\eqref{eqn:optcond2}, and~\eqref{eqn:optcond3} into the Lagrangian in~\eqref{eqn:svmlagrangian}, the dual MIRSVM formulation becomes the following:
\begin{subequations} 
\label{eq:dualmirsvm1}
\begin{alignat}{2}
\max\limits_{\bm \alpha,\bm \beta}& \sum_I \alpha_I -\frac{1}{2}\sum_I \sum_{K\in I} \sum_{j=1}^d \alpha_I \alpha_K Y_I Y_K  x_{s_I j} x_{s_K j} \tag{\ref{eq:dualmirsvm1}}\\
\text{s.t.}&  \sum_I{\alpha_IY_I} = 0\, \\
{} & \alpha_I + \beta_I = \frac{C}{n},\,\forall I \in \set{1,\ldots,n}   \label{eq:implicit1}\\
{} & \alpha_I \geq 0,\, \forall I \in \set{1,\ldots,n}  \label{eq:implicit2} \\
{} & \beta_I \geq 0,\, \forall I \in \set{1,\ldots,n},  \label{eq:implicit3}
\end{alignat}
\end{subequations} 
where $s_I$ is computed for each bag, as shown in Equation~\eqref{eq:si}:
\begin{equation}
\label{eq:si}
\centering
s_I = \underset{i \in I}{\text{argmax}}(\sum_{K\in I} \sum_{j=1}^d \alpha_K Y_K x_{s_K j} x_{ij} + b),\, \forall I \in \set{1,\ldots,n}.
\end{equation}

>>>>

\section{Introduction}\label{intro}
In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns between training samples and their class label. \textit{Multi-instance} (MI) learning is a generalization of \textit{supervised learning} that has been recently been gaining interest because \hl{of its applicability to many real-world problems such as webmining and text categorization {\citep{Andrews2002}}, image classification and retreival} {\citep{qi2007,cao2017weakly}}, \hl{human action recognition {\citep{Yi2016}}, medical diagnosis and imaging {\citep{Herrera2016}}, and bioinformatics {\citep{Dietterich1997}} (drug activity prediction and protein identification).}

@@

For most of the methods described above, implicit or explicit assumptions have been made about the distribution of the data~\citep{2017-KNOSYS-MIMV}. Selecting a method that is robust for a problem such as MIL can be difficult when little is known about the nature of the data, especially considering the unknown distribution of the instances within bags~\citep{2015-KAIS,2016-INS-MIARM}. \hl{MIRSVM, is an iterative method that uses SVMs to design a MIL model without making prior assumptions about the data. Classifiers of this type are known to provide better generalization capabilities, performance, and sparser models.}

@@

\section{Multiple-Instance Representative SVM}\label{sec:contribution}
MIRSVM is based on the idea of selecting representative instances from both positive and negative bags which are used to find an unbiased, optimal separating hyperplane. A representative is iteratively chosen from each bag, and a new hyperplane is formed according to the representatives until they converge. Based on the SMI hypothesis, only one instance in a bag is required to be positive for the bag to adopt a positive label. \hl{Due to the unknown distribution of instances within positive bags, MIRSVM is designed to give preference to negative bags during training, because their distribution is known, i.e. all instances are guaranteed to be negative. This is evident during the representative selection process, by taking the index of the maximum output value within each bag based on the current hyperplane using the following rule:}
\begin{equation}
\label{eq:SIPrimal}
\centering
s_I = \text{argmax}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n},
\end{equation}
\hl{where $\bm w \in \reals^d$ is a $d$-dimensional weight vector, $b \in \reals$ is a bias term.} In other words, the most positive instance is chosen from each positive bag and the least negative instance is chosen from each negative bag (instances with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags. Equation~\eqref{eq:primalmirsvm} presents the primal MIRSVM optimization problem:
\begin{subequations} 
\label{eq:primalmirsvm}
\begin{alignat}{2}
\min\limits_{\bm w, b,\bm\xi}& {\,\,} \frac{1}{2}||\bm{w}||^2 + \frac{C}{n}\sum_I \xi_I, \tag{\ref{eq:primalmirsvm}}\\ 
\text{s.t.}& {\,\,} Y_I(\langle\bm{w},\bm x_{s_I}\rangle + b) \geq 1 - \xi_I,\, \forall I \in \set{1,\ldots,n}  \label{eq:primalmirsvm1}\\
{} & {\,\,} \xi_I \geq 0,\, \forall I \in \set{1,\ldots,n}, 
\end{alignat}
\end{subequations} 
\hl{where $\bm S_I$ is a set of the bag representatives' indices, $\bm x_{s_I}$ is the instance representative of bag $\mathcal{B}_I$, and the slack variable $\bm \xi \in \reals^m$ allows for optimizing over bag errors. Note the variables in MIRSVMs formulation are the similar to those of the traditional SVM, except they are now representing each bag as an instance. This is one of the benefits of the MIRSVM formulation, whereby using a bag-representative selector, traditional SVM solvers can be used for new data representations such the multi-instance data.}

Solving the optimization problem given in Equation~\eqref{eq:primalmirsvm} using a quadratic programming solver is a computationally expensive task due to the number of constraints, which scales by the number of bags $n$, as well as the calculation of the inner product between two $d$-dimensional vectors in constraint~\eqref{eq:primalmirsvm1}. The proposed solution for these problems was deriving and solving the dual of the optimization problem given by Equation~\eqref{eq:primalmirsvm}.

\hl{The dual can be formed by taking the Lagrangian of~{\eqref{eq:primalmirsvm}}, $\mathcal{L}(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta})$, and substituting the optimality conditions (from $\bigtriangledown_{w,b,\xi}\mathcal{L}(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}) = 0$), where $\bm \alpha$ and $\bm \beta$ are the non-negative Lagrange multipliers. The dual MIRSVM formulation becomes the following:}
\begin{subequations} 
\label{eq:dualmirsvm1}
\begin{alignat}{2}
\max\limits_{\bm \alpha,\bm \beta}& \sum_I \alpha_I -\frac{1}{2}\sum_I \sum_{K\in I} \sum_{j=1}^d \alpha_I \alpha_K Y_I Y_K  x_{s_I j} x_{s_K j} \tag{\ref{eq:dualmirsvm1}}\\
\text{s.t.}&  \sum_I{\alpha_IY_I} = 0\, \\
{} & \alpha_I + \beta_I = \frac{C}{n},\,\forall I \in \set{1,\ldots,n}   \label{eq:implicit1}\\
{} & \alpha_I \geq 0,\, \forall I \in \set{1,\ldots,n}  \label{eq:implicit2} \\
{} & \beta_I \geq 0,\, \forall I \in \set{1,\ldots,n},  \label{eq:implicit3}
\end{alignat}
\end{subequations} 
where $s_I$ is computed for each bag, as shown in Equation~\eqref{eq:si}:
\begin{equation}
\label{eq:si}
\centering
s_I = \underset{i \in I}{\text{argmax}}(\sum_{K\in I} \sum_{j=1}^d \alpha_K Y_K x_{s_K j} x_{ij} + b),\, \forall I \in \set{1,\ldots,n}.
\end{equation}

### 2017-09-19 ArticleRevision/article_with_markings/letter/letter.tex
Made changes according to Alberto + ran spell checker. Going to copy these to dropbox so he can submit it later.

\noindent Answer...

@@

\noindent Answer...

@@

\noindent The answer...

@@

\noindent Answer...

@@

\noindent Answer...

\noindent \textbf{\textit{Comment 2: However, according to me, I think the technical novelty is somewhat marginal. 
The formulations in section 3 are all standard SVM, except that it now operates at the bag-level. The only (technical) contribution I see is the new measure used to select bag representatives. And this contribution should be highlighted. }}

@@

\noindent Answer...

@@

\noindent Answer...

@@

\noindent Answer...

@@

\noindent Answer...

@@

\noindent Thank you for pointing out that statement. What we meant was that they assume that all the instances within positive bags are assumed to be positive, or to follow the distribution of positively labelled data.

@@

\noindent We apologize for the ambiguity. What we were specifying was the MIRSVM bag-representative selector and formutlation. We've made the appropriate change in text.

@@

\noindent Answer...

@@

\noindent Answer...

@@

\noindent Answer...

>>>>

\noindent We appreciate the reivewer's comments on the background we have given to present our contribution.

@@

\noindent We tried our best to provide a comprehensive and detailed explanation of our contribution, and we thank the reviewers for their positive comments on this.

@@

\noindent Again, we would like to express our gratitude on the reviewer's positive comments about our contribution and experimental study. We wanted to be as clear as possible when highlighting the differences between our method and the state-of-the-art methods, and Figure 4 was one of the ways to show how selecting representatives from one class and not the other can prove to be biased. So, we thank the reviewer on aknowledging this.

@@

\noindent We thank and appreciate the reviewer for the positive and constructive comments given towards improving this paper.

@@

\noindent We tried to be as thorough as possible during our experimental study and we intend on continuing with this method of experimentation. We really appreciate your comment on this.

\noindent \textbf{\textit{Comment 2: However, according to me, I think the technical novelty is somewhat marginal. The formulations in Section 3 are all standard SVM, except that it now operates at the bag-level. The only (technical) contribution I see is the new measure used to select bag representatives. And this contribution should be highlighted. }}

@@

\noindent We took your advice on this and removed some of the standard SVM formulations in Section 3 (specifically the Langrangian and derivation of the dual), highlighted the bag-representative selector, as well as emphasized the major benefits using it in conjunction with the bag level formulation of the SVM. Therefore, this way we enhance and clarify the benefits of the contribution, without having redundant information within the section.

@@

\noindent We rewrote and reorganized Sections 1, 2, and 3 to condense the information given. We shortened and rewrote some of the descriptions on the background of multiple-instance learning, as well as removed some of the basic SVM formulations from the background to avoid repetition in Section 3. Your comment on the length of those sections makes sense, thank you.

@@

\noindent Thank you for noting this. As you have suggested, we added a couple of additional applications of the standard MI assumption to the paper. Specifically, the following real-world scenarios provide a more global picture as to why MI algorithms are useful: bioinformatics (protein identification), image classification \& retrieval, web mining \& text classification, and medical diagnosis \& imaging.

@@

\noindent According to your suggestion, we tested the performance of our method using a wider range of parameters (especially with lower C values). Results were exactly the same as originally reported, since the best parameters were still selected in the domain we originally defined. The only difference of evaluating a larger number of parameters would be a longer runtime, but we observed no performance difference in the results for any of the datasets evaluated. Thank you.

@@

\noindent Thank you for pointing out that statement. What we meant was that they assume that all the instances within positive bags are assumed to be positive, or to follow the distribution of positively labelled data. This statement was clarified in the text.

@@

\noindent We apologize for the ambiguity. What we were specifying was the MIRSVM bag-representative selector and formulation, referenced by Equations 12 and 13. We have made the appropriate change in text to clarify the meaning.

@@

\noindent We've updated the text to the correct grammar. Thank you.

@@

\noindent Thank you for making note of that. We have updated the text to be ``Gram matrix".

@@

\noindent Thank you for your comprehensive notes and constructive comments on our paper.
